#==============================================================================
# RCS Header:
#   File         [$Source: /home/hc0300/umui/srce_code/GHUI_archive/ghui2.0/doc/GHUI_doc.tex,v $]
#   Revision     [$Revision: 1.2 $]     Named [$Name: head#main $]
#   Last checkin [$Date: 2000/10/16 14:24:06 $]
#   Author       [$Author: hadsm $]
#==============================================================================

\documentclass{report}
\usepackage[dvips]{graphicx}
\begin{document}
\begin{titlepage}
\begin{center}
\textbf{The General Hierarchical User Interface}
\ \\
S.D.Mullerworth \\
\ \\
Version 1.0 \\
\ \\
20th October 2000 \\
\ \\
GHUI version 2.0. Navigation System version 1.2

\vspace{2.5in}
Climate Research \\
The Met. Office \\
London Road \\
BRACKNELL \\
Berkshire \\
RG12 2SY \\
United Kingdom

\vspace{0.5in}
(c) Crown Copyright 2000
\par
\ \\
This document has not been published. Permission to quote from
it must be obtained from the Head of Climate Prediction at the above address.
\end {center}

\end{titlepage}

\tableofcontents
\chapter{Modification History}

  \begin{center}
  \begin{tabular}{|c|c|c|p{0.25\hsize}|}           \hline
  \textbf{Date} & \textbf{Author} & \textbf{UM version}
  & \textbf{Description of change} \\ \hline

    20 October 2000 &  S.D.Mullerworth & 5.0 &
    Original. \\ \hline

  \end{tabular}
  \end{center}

\chapter{Introduction}

The Generic Hierarchical User Interface, or GHUI, is a package that
allows the creation of large forms based user interfaces. It is the
package that underlies user interfaces developed at the Met. Office
such as the UMUI, VARUI and SCSUI.

The GHUI allows the user interface developer to write input panels
using a simple language. Panels are presented to users in a tree
hierarchy to help them find their way to the appropriate panel or
setup panel. Validation of user input is performed to reduce the
number of user errors. Once setup is completed by the user a
processing function converts the input into a suitable output as
prescribed by the user interface developer.

Users may own many separate job setups. The GHUI incorporates code for
setting up a central job database in which all jobs owned by all users
is stored. Jobs are accessed via a client/server system.

The functionality provided by the GHUI aims to be reasonably
comprehensive but also aims to be extendible; where the GHUI functions
do not provide a comletely appropriate validation check or panel
design an alternative one can be provided. Some knowledge of Tcl and
Tk may be required to implement such extensions.

This document incorporates both system documentation, documentation
required to develop new user interfaces and documentation required to
install and manage user interfaces. Firstly, an overview of the
look-and-feel of a typical GHUI based user interface is given.

\input{overviewDoc.tex}
\input{sysManageDoc.tex}
\input{userDoc.tex}
\input{systemDoc.tex}
\end{document}
